The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Add packages related to networks in the setup code chunk

# Load packages ----
## Managing paths
library(here)

## Data manipulation and visualisation
library(tidyverse)

## Text processing and analysis
library(tidytext)
library(SnowballC)
library(tm)
library(topicmodels)

## Working with spatial data
library(tidygeocoder)

@@

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

emu_theses$text_clean <- emu_theses$text |> 
  clean_basic() |> 
  str_remove_all(find_meta_stopwords(emu_theses) )  
```

@@

A total number of `r nrow(emu_theses)` out of `r nrow(theses_all)` were analysed.

@@

## Topic model

Similar to topic clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017].

@@

emu_theses_bigrams_top_all <- emu_theses_bigrams %>%
  count(bigram, sort = TRUE) %>%
  slice_max(n, n = 20) %>%        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(bigram = reorder(bigram, n))

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                         # Managing paths
  "tidyverse",                    # Data manipulation and visualisation
  "tidytext", "SnowballC", "tm",  # Text processing and analysis
  "tidygeocoder",                 # Working with spatial data
  "igraph", "ggraph"              # Network analysis and visualsation
)

## Load required packages, install them if needed
for (package in packages) {
  if (!require(package, character.only = TRUE)) {
    install.packages(package)
  }
  library(package, character.only = TRUE)
}

@@

```{r}
#| label: extract-pdf-text
#| echo: false

# Extract text from PDFs
# On the first run, this function might take extra time as a Python environment needs to be set up
emu_theses$text <- convert_pdf_text(pdf_paths)
```

@@

#head_text(emu_theses$text)

# clean text 
emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )

```

@@

A total number of `r nrow(emu_theses)` were analysed.

@@

@@
